Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2015-08-11 writeup/gz_hubble_data.tex
fixed table 4

\begin{table}
\caption{Debiasable Hubble Stuff. Doesn't include SDSS yet. Note: stuff without good redshift info automatically gets put in uncorrectable category - which is about 25,000 galaxies. Might increase correctable number if we can get these measurements. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
\hline
Correctable                        & 2,438   & 21,522 & 28,52 & 1,146  & 1,040   & 0       & 28,998\\
Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
No Correction Needed ($z \le 0.3$) & 854     & 10,840 & 1,086 & 208    & 229     & 37,545  & 50,762\\ 
NEI                                & 2,464   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,791\\
No Redshift Information            & 1,348   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,281\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
\hline\hline
\end{tabular}
\end{table}

>>>>

\begin{table*}
\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
\hline
Correctable                        & 2,438   & 21,522 & 28,52 & 1,146  & 1,040   & 0       & 28,998\\
Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
No Correction Needed ($z \le 0.3$) & 698     & 9,679 & 1,012 & 171    & 199     & 37,545  & 50,762\\ 
NEI                                & 2,621   & 34,888 & 1,960 & 728    & 2,053   & 0       & 40,791\\
No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,281\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
\hline\hline
\end{tabular}
\end{table*}
